---
title: "Final Project"
author: "B. Pritchard"
date: "2022-11-23"
output:
  html_document: default
  pdf_document: default
---

The purpose of this R program is to recreate and evaluate a couple of the key results and tables from the paper "The empirical relationship between nonstandard economic behaviors" by Mark Dean and Pietro Ortoleva, the paper, data set, and supporting documents are located at: https://www.pnas.org/doi/full/10.1073/pnas.1821353116

```{r}
library(knitr)
library(formatR)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=120),tidy='styler')
```


#### Opening packages and reading in the data
```{r}
library(tidyverse)
library(ivreg)
library(gt)
library(gtsummary)
library(data.table)
library(corrr)
library(describedata)
library(psych)

df <- read.csv("C:/Users/bradl/OneDrive/Desktop/Fall_2022/Linear_Reg_Analysis/Data_LRA/pnas.1821353116.sd01.csv")
#View(df)
#names(df)
dim(df)
```


#### Table 1 features selection and descriptive statistics
```{r}
tab_1_feats <- df %>% select("discount_rate_pcf",
                             "present_discount_rate_pcf",
                             "risk_pcf",
                             "allais_pcf",
                             "common_l_pcf",
                             "uncertainty_pcf",
                             "compound_pcf",
                             "m_risk",
                             "b_risk_pcf",
                             "trust",
                             "return",
                             "raven_total",
                             "overconfidence_1",
                             "overconfidence_2",
                             "gender",
                             "anxiety",
                             "depression")
#str(tab_1_feats)

# Function that gathers various descriptive statistics
get_descriptive_stats <- function(data){
                                
  summary_data <- summary(na.omit(data)) # summarize data
  sd_data <- sd(na.omit(data)) # standard deviation of data
  var_data <- var(na.omit(data)) # variance of data
  iqr_data <- IQR(na.omit(data)) # inter quartile range of data
  descriptive_stats <- c(summary_data,
                         "Standard Deviation" = sd_data,
                         "Variance" = var_data,
                         "IQR" = iqr_data) # combine descriptive stats and
                                           # label each statistic accordingly
  return(round(descriptive_stats, digits = 4))

}

desc_stats_t1 <- apply(tab_1_feats, 2, get_descriptive_stats) %>%
  data.table(keep.rownames = TRUE)
print(desc_stats_t1)
```

#### Setting up correlation matrix for Table 1
```{r}
stats_tab1 <- corr.test(tab_1_feats,
                        use = "pairwise",
                        method = "pearson",
                        adjust = "none",
                        alpha = 0.01)

stats_tab2 <- corr.test(tab_1_feats,
                        use = "pairwise",
                        method = "pearson",
                        adjust = "none",
                        alpha = 0.01)

stats_tab3 <- round(stats_tab2$r, digits = 2)
stats_tab3[upper.tri(stats_tab3, diag = FALSE)] <- " "

cor_mat_tab1 <- data.table(stats_tab3, keep.rownames = TRUE)

cor_mat_tab1 <- as.data.frame(cor_mat_tab1)

rows <- nrow(cor_mat_tab1)

cor_mat_tab1[rows + 16, ] <- NA

t_stats_tab1 <- data.table(round(stats_tab1$t,
                                 digits = 2),
                           keep.rownames = TRUE)
```

Adding the t-statistics to the Table 1 correlation matrix
```{r}
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 18L:33L,
                        j = 2L,
                        value = t_stats_tab1[2:17, 2])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 18L,
                        j = 3L,
                        value = NA)
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 19L,
                        j = 3L,
                        value = t_stats_tab1[3, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 20L,
                        j = 3L,
                  value = t_stats_tab1[4, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 21L,
                        j = 3L,
                        value = t_stats_tab1[5, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 22L,
                        j = 3L,
                        value = t_stats_tab1[6, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 23L,
                        j = 3L,
                        value = t_stats_tab1[7, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 24L,
                        j = 3L,
                        value = t_stats_tab1[8, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 25L,
                        j = 3L,
                        value = t_stats_tab1[9, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 26L,
                        j = 3L,
                        value = t_stats_tab1[10, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 27L,
                        j = 3L,
                        value = t_stats_tab1[11, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 28L,
                        j = 3L,
                        value = t_stats_tab1[12, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 29L,
                        j = 3L,
                        value = t_stats_tab1[13, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 30L,
                        j = 3L,
                        value = t_stats_tab1[14, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 31L,
                        j = 3L,
                        value = t_stats_tab1[15, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 32L,
                        j = 3L,
                        value = t_stats_tab1[16, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 33L,
                        j = 3L,
                        value = t_stats_tab1[17, 3])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 20L:33L,
                        j = 4L,
                        value = t_stats_tab1[4:17, 4])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 21L:33L,
                        j = 5L,
                        value = t_stats_tab1[5:17, 5])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 22L:33L,
                        j = 6L,
                        value = t_stats_tab1[6:17, 6])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 23L:33L,
                        j = 7L,
                        value = t_stats_tab1[7:17, 7])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 24L:33L,
                        j = 8L,
                        value = t_stats_tab1[8:17, 8])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 25L:33L,
                        j = 9L,
                        value = t_stats_tab1[9:17, 9])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 26L:33L,
                        j = 10L,
                        value = t_stats_tab1[10:17, 10])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 27L:33L,
                        j = 11L,
                        value = t_stats_tab1[11:17, 11])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 28L:33L,
                        j = 12L,
                        value = t_stats_tab1[12:17, 12])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 29L:33L,
                        j = 13L,
                        value = t_stats_tab1[13:17, 13])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 30L:33L,
                        j = 14L,
                        value = t_stats_tab1[14:17, 14])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 31L:33L,
                        j = 15L,
                        value = t_stats_tab1[15:17, 15])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 32L:33L,
                        j = 16L,
                        value = t_stats_tab1[16:17, 16])
cor_mat_tab1_v2 <- set(cor_mat_tab1,
                        i = 33L:33L,
                        j = 17L,
                        value = t_stats_tab1[17, 17])
```


#### Table 1 Creation
```{r}
tru_order <- c(1, 2, 18, 3, 19, 4, 20, 5, 21, 6,
               22, 7, 23, 8, 24, 9, 25, 10, 26, 11,
               27, 12, 28, 13, 29, 14, 30, 15, 31,
               16, 32, 17, 33)

setroworder <- function(x, neworder) {
    .Call(data.table:::Creorder, x, as.integer(neworder), PACKAGE = "data.table")
    invisible(x)
}
# from: https://stackoverflow.com/questions/37878620/reorder-rows-in-data-table-in-a-specific-order

setroworder(cor_mat_tab1_v2, tru_order)

cor_mat_tab1_v2 <- cor_mat_tab1_v2[, -c(1)]
class(cor_mat_tab1_v2)

names(cor_mat_tab1_v2) <- c("Discount ",
                            "Present discount",
                            "Risk aversion",
                            "C. consequence",
                            "C. ratio",
                            "Uncertainty",
                            "Compound",
                            "Mixed Risk",
                            "Buy Risk",
                            "Send",
                            "Return",
                            "Intelligence",
                            "Overconf.",
                            "Overplace",
                            "Gender",
                            "Anxiety",
                            "Depression")

row.names(cor_mat_tab1_v2) <- c("Discount",
                                "Present discount",
                                " ",
                                "Risk aversion",
                                "  ",
                                "C. consequence",
                                "   ",
                                "C. ratio",
                                "    ",
                                "Uncertainty At.",
                                "     ",
                                "Compound At.",
                                "      ",
                                "Mixed Risk",
                                "       ",
                                "Buy Risk",
                                "        ",
                                "Trust-send",
                                "         ",
                                "Trust-return",
                                "          ",
                                "Intelligence",
                                "           ",
                                "Overconfidence",
                                "            ",
                                "Overplacement",
                                "             ",
                                "Gender",
                                "              ",
                                "Anxiety",
                                "                ",
                                "Depression",
                                "                 ")
cor_mat_tab1_v2[is.na(cor_mat_tab1_v2)] <- " "

cor_mat_tab1_v2[3, 1] <- paste0(format(unlist(cor_mat_tab1_v2[3, 1])), "***")
cor_mat_tab1_v2[5, 2] <- paste0(format(unlist(cor_mat_tab1_v2[5, 2])), "***")
cor_mat_tab1_v2[7, 3] <- paste0(format(unlist(cor_mat_tab1_v2[7, 3])), "***")
cor_mat_tab1_v2[9, 3] <- paste0(format(unlist(cor_mat_tab1_v2[9, 3])), "*")
cor_mat_tab1_v2[9, 4] <- paste0(format(unlist(cor_mat_tab1_v2[9, 4])), "***")
cor_mat_tab1_v2[11, c(1, 2, 4)] <- paste0(format(unlist(cor_mat_tab1_v2[11,
                                                          c(1, 2, 4)])), "*")
cor_mat_tab1_v2[11, 3] <- paste0(format(unlist(cor_mat_tab1_v2[11, 3])), "***")
cor_mat_tab1_v2[11, 5] <- paste0(format(unlist(cor_mat_tab1_v2[11, 5])), "**")
cor_mat_tab1_v2[13, c(1, 2, 5)] <- paste0(format(unlist(cor_mat_tab1_v2[13,
                                                          c(1, 2, 5)])), "*")
cor_mat_tab1_v2[13, c(3, 6)] <- paste0(format(unlist(cor_mat_tab1_v2[13,
                                                          c(3, 6)])), "***")
cor_mat_tab1_v2[13, 4] <- paste0(format(unlist(cor_mat_tab1_v2[13, 4])), "**")
cor_mat_tab1_v2[15, 5] <- paste0(format(unlist(cor_mat_tab1_v2[15, 5])), "**")
cor_mat_tab1_v2[15, c(2, 3, 5)] <- paste0(format(unlist(cor_mat_tab1_v2[15,
                                                          c(2, 3, 5)])), "**")
cor_mat_tab1_v2[15, c(4, 7)] <- paste0(format(unlist(cor_mat_tab1_v2[15,
                                                             c(4, 7)])), "*")
cor_mat_tab1_v2[17, c(2, 4, 5)] <- paste0(format(unlist(cor_mat_tab1_v2[17,
                                                          c(2, 4, 5)])), "*")
cor_mat_tab1_v2[17, c(3, 7, 8)] <- paste0(format(unlist(cor_mat_tab1_v2[17,
                                                        c(3, 7, 8)])), "***")
cor_mat_tab1_v2[17, 6] <- paste0(format(unlist(cor_mat_tab1_v2[17, 6])), "**")
cor_mat_tab1_v2[21, 8] <- paste0(format(unlist(cor_mat_tab1_v2[21, 8])), "**")
cor_mat_tab1_v2[21, 10] <- paste0(format(unlist(cor_mat_tab1_v2[21, 10])),
                                                                        "***")
cor_mat_tab1_v2[23, 1] <- paste0(format(unlist(cor_mat_tab1_v2[23, 1])), "**")
cor_mat_tab1_v2[23, 9] <- paste0(format(unlist(cor_mat_tab1_v2[23, 9])), "*")
cor_mat_tab1_v2[27, c(1, 4, 6)] <- paste0(format(unlist(cor_mat_tab1_v2[27,
                                                           c(1, 4, 6)])), "*")
cor_mat_tab1_v2[27, c(8, 9)] <- paste0(format(unlist(cor_mat_tab1_v2[27,
                                                             c(8, 9)])), "***")
cor_mat_tab1_v2[29, c(8, 9)] <- paste0(format(unlist(cor_mat_tab1_v2[29,
                                                             c(8, 9)])), "***")

tab1_gt <- gt(cor_mat_tab1_v2,
              rownames_to_stub = TRUE,
              auto_align = "FALSE")
tab1_gt <- tab1_gt %>% 
  tab_header(title = md("**Table 1. Correlation between behaviors**")) %>%
  opt_align_table_header(align = c("left")) %>%
  cols_hide(columns = c("Intelligence",
                        "Overconf.",
                        "Overplace",
                        "Gender",
                        "Anxiety",
                        "Depression")) %>%
  tab_source_note(source_note = ("*, significant at the 0.05 level; **, significant at the 0.01 level; ***, significant at the 0.001 level (uncorrected for multiple comparisons). In each row, top cell shows correlation coefficient between row and column variable. Bottom cell shows associated t statistic. Gender coded 0 = male, 1 = female. C., Common; at., attitude."))

tab1_gt

tab1_gt %>% gtsave(filename = "tab1_gt_fall_2022.html")
```


#### Table 4 2SLS Regressions
```{r}
relevant_dat <- df %>% select("end_new_pcf", "loss_aversion", "raven_total", "risk_pcf", "common_l_pcf", "allais_pcf", "ambiguity_pcf", "common_l_1", "common_l_2", "allais_1", "allais_2", "risk_pcf", "reduction_pcf", "ambiguity_1", "ambiguity_2", "ambiguity_3",  "discount_rate_pcf", "present_discount_rate_pcf", "present_bias_pcf", "risk_1", "overconfidence_1", "overconfidence_2", "end_new_1", "end_new_2", "end_new_3", "end_new", "loss_aversion", "raven_total", "risk", "common_l", "allais", "ambiguity", "reduction", "ambiguity_1", "ambiguity_2", "ambiguity_3", "discount_rate", "present_discount_rate", "present_bias", "risk_1", "risk_2", "risk_3", "end_new_1_i", "end_new_2_i", "end_new_3_i", "loss_aversion_i", "common_l_1_i", "common_l_2_i", "allais_1_i", "allais_2_i", "ambiguity_i", "uncertainty_i", "risk_1_i", "risk_2_i", "risk_3_i", "compound_i", "reduction_i", "reduction_1_i", "reduction_2_i", "reduction_3_i", "b_risk_i", "ambiguity_1_i", "ambiguity_2_i", "ambiguity_3_i", "end_new_i", "present_bias_i", "risk_i", "discount_rate_i", "present_discount_rate_i", "trust", "return", "common_l_i", "allais_i", "compound_1_i", "compound_2_i", "compound_3_i", "anxiety", "depression", "alt_risk_pcf", "alt_risk", "alt_risk_1", "alt_risk_2", "alt_risk_3", "alt_risk_i", "alt_risk_1_i", "alt_risk_2_i", "alt_risk_3_i", "gender", "backwards", ) %>% data.table()

#str(relevant_dat)
scale_dat <- scale(relevant_dat)

# Normalized data to mean = 0, sd = 1 as was done by the authors of the paper.
renormalized_dat <- data.table(scale_dat)
class(renormalized_dat)

```


#### Descriptive statistics of features used in Table 4
```{r}
tab4_feats <- renormalized_dat %>% select("risk_1_i",
                                          "common_l_1_i",
                                          "allais_1_i",
                                          "end_new_1_i",
                                          "loss_aversion_i",
                                          "compound_1_i",
                                          "raven_total",
                                          "gender",
                                          "risk_2_i",
                                          "risk_3_i",
                                          "common_l_2_i",
                                          "allais_2_i",
                                          "end_new_2_i",
                                          "end_new_3_i",
                                          "compound_2_i",
                                          "compound_3_i")

desc_stats_t4 <- apply(tab4_feats, 2, get_descriptive_stats) %>%
  data.table(keep.rownames = TRUE)

desc_stats_t4 <- t(desc_stats_t4) %>% data.frame()
desc_stats_t4 <- desc_stats_t4[-1, ]
names(desc_stats_t4) <- c("Min.",
                          "1st Qu.",
                          "Median",
                          "Mean",
                          "3rd Qu.",
                          "Max.",
                          "Std. Dev",
                          "Variance",
                          "IQR")
print(desc_stats_t4)
```


#### Running the five separate 2SLS regressions for Table 4
```{r}
col1_tab_4_2sls <- ivreg(formula = uncertainty_i ~ risk_1_i +
                                                   common_l_1_i +
                                                   allais_1_i +
                                                   end_new_1_i +
                                                   loss_aversion_i +
                                                   raven_total +
                                                   gender +
                                                   backwards | raven_total +
                                                   gender +
                                                   backwards +
                                                   risk_2_i +
                                                   risk_3_i +
                                                   common_l_2_i +
                                                   allais_2_i +
                                                   end_new_2_i +
                                                   end_new_3_i +
                                                   loss_aversion_i,
                                                   data = renormalized_dat)
summary(col1_tab_4_2sls)

col2_tab_4_2sls <- ivreg(formula = ambiguity_i ~ risk_1_i +
                                                 common_l_1_i +
                                                 allais_1_i +
                                                 end_new_1_i +
                                                 loss_aversion_i +
                                                 raven_total +
                                                 gender +
                                                 backwards | raven_total +
                                                 gender +
                                                 backwards +
                                                 risk_2_i +
                                                 risk_3_i +
                                                 common_l_2_i +
                                                 allais_2_i +
                                                 end_new_2_i +
                                                 end_new_3_i +
                                                 loss_aversion_i,
                                                 data = renormalized_dat)
summary(col2_tab_4_2sls)

col3_tab_4_2sls <- ivreg(formula = compound_i ~ risk_1_i +
                                                common_l_1_i +
                                                allais_1_i +
                                                end_new_1_i +
                                                loss_aversion_i +
                                                raven_total +
                                                gender +
                                                backwards | raven_total +
                                                gender +
                                                backwards +
                                                risk_2_i +
                                                risk_3_i +
                                                common_l_2_i +
                                                allais_2_i +
                                                end_new_2_i +
                                                end_new_3_i +
                                                loss_aversion_i,
                                                data = renormalized_dat)
summary(col3_tab_4_2sls)

col4_tab_4_2sls <- ivreg(formula = reduction_i ~ risk_1_i +
                                                 common_l_1_i +
                                                 allais_1_i +
                                                 end_new_1_i +
                                                 loss_aversion_i +
                                                 raven_total +
                                                 gender +
                                                 backwards | raven_total +
                                                 gender +
                                                 backwards +
                                                 risk_2_i +
                                                 risk_3_i +
                                                 common_l_2_i +
                                                 allais_2_i +
                                                 end_new_2_i +
                                                 end_new_3_i +
                                                 loss_aversion_i,
                                                 data = renormalized_dat)
summary(col4_tab_4_2sls)

col5_tab_4_2sls <- ivreg(formula = ambiguity_i ~ risk_1_i +
                                                 common_l_1_i +
                                                 allais_1_i +
                                                 end_new_1_i +
                                                 loss_aversion_i +
                                                 compound_1_i +
                                                 raven_total +
                                                 gender +
                                                 backwards | raven_total +
                                                 gender +
                                                 backwards +
                                                 risk_2_i +
                                                 risk_3_i +
                                                 common_l_2_i +
                                                 allais_2_i +
                                                 end_new_2_i +
                                                 end_new_3_i +
                                                 compound_2_i +
                                                 compound_3_i +
                                                 loss_aversion_i,
                                                 data = renormalized_dat)
summary(col5_tab_4_2sls)
# Applied to 2SLS regression, the Wu–Hausman test is a test of endogenity. If all of the regressors are exogenous, then both the OLS and 2SLS estimators are consistent, and the OLS estimator is more efficient, but if one or more regressors are endogenous, then the OLS estimator is inconsistent. A large test statistic and small p-value, as in the example, suggests that the OLS estimator is inconsistent and the 2SLS estimator is therefore to be preferred.
```


#### Table 4 Creation
```{r}
col1_coefs <- data.frame(summary(col1_tab_4_2sls)$coefficients[2:9, 1],
                         summary(col1_tab_4_2sls)$coefficients[2:9, 2])
col1_new <- col1_coefs[-c(6, 7, 8, 9), ]

col2_coefs <- data.frame(summary(col2_tab_4_2sls)$coefficients[2:9, 1],
                         summary(col2_tab_4_2sls)$coefficients[2:9, 2])
col2_new <- col2_coefs[-c(6, 7, 8, 9), ]

col3_coefs <- data.frame(summary(col3_tab_4_2sls)$coefficients[2:9, 1],
                         summary(col3_tab_4_2sls)$coefficients[2:9, 2])
col3_new <- col3_coefs[-c(6, 7, 8, 9), ]

col4_coefs <- data.frame(summary(col4_tab_4_2sls)$coefficients[2:9, 1],
                         summary(col4_tab_4_2sls)$coefficients[2:9, 2])
col4_new <- col4_coefs[-c(6, 7, 8, 9), ]

col5_coefs <- data.frame(summary(col5_tab_4_2sls)$coefficients[2:10, 1],
                         summary(col5_tab_4_2sls)$coefficients[2:10, 2])
col5_new <- col5_coefs[-c(7, 8, 9), ]

col1_stack <- stack(col1_new)
new_order1 <- c(1, 6, 2, 7, 3, 8, 4, 9, 5, 10)
setroworder(col1_stack, new_order1)
col1 <- col1_stack[, -c(2)]

col2_stack <- stack(col2_new)
new_order2 <- c(1, 6, 2, 7, 3, 8, 4, 9, 5, 10)
setroworder(col2_stack, new_order2)
col2 <- col2_stack[, -c(2)]

col3_stack <- stack(col3_new)
new_order3 <- c(1, 6, 2, 7, 3, 8, 4, 9, 5, 10)
setroworder(col3_stack, new_order3)
col3 <- col3_stack[, -c(2)]

col4_stack <- stack(col4_new)
new_order4 <- c(1, 6, 2, 7, 3, 8, 4, 9, 5, 10)
setroworder(col4_stack, new_order4)
col4 <- col4_stack[, -c(2)]

col5_stack <- stack(col5_new)
new_order5 <- c(1, 7, 2, 8, 3, 9, 4, 10, 5, 11, 6, 12)
setroworder(col5_stack, new_order5)
col5 <- col5_stack[, -c(2)]

tab_4 <- data.table(col1, col2, col3, col4, col5)
tab_4 <- data.frame(tab_4)
row.names(tab_4) <- c("Risk Aversion",
                      " ",
                      "Common Ratio",
                      "  ",
                      "Common Conseq.",
                      "   ",
                      "Endowment Effect",
                      "    ",
                      "Loss Aversion",
                      "     ",
                      "Compound Av.",
                      "      ")
rnd_tab4 <- round(tab_4, digits = 5)

true_tab4 <- set(rnd_tab4,
                 i = 11L:12L,
                 j = 1L:4L,
                 value = " ")
true_tab4[is.na(true_tab4)] <- " "

true_tab4[c(2, 4, 6, 8, 10), ] <- paste0("(",
                                         format(unlist(true_tab4[c(2, 4, 6,
                                                                   8, 10),
                                                                 ])),")")
true_tab4[12, 5] <- paste0("(",format(unlist(true_tab4[12, 5])),")")
true_tab4[1, 1] <- paste0(format(unlist(true_tab4[1, 1])), "****")
true_tab4[1, 2] <- paste0(format(unlist(true_tab4[1, 2])), "**")
true_tab4[1, 3] <- paste0(format(unlist(true_tab4[1, 3])), "****")
true_tab4[1, 4] <- paste0(format(unlist(true_tab4[1, 4])), "*")
true_tab4[7, 1] <- paste0(format(unlist(true_tab4[7, 1])), "**")
true_tab4[7, 2] <- paste0(format(unlist(true_tab4[7, 2])), "**")
true_tab4[7, 3] <- paste0(format(unlist(true_tab4[7, 3])), "**")
true_tab4[7, 4] <- paste0(format(unlist(true_tab4[7, 4])), "***")
true_tab4[11, 5] <- paste0(format(unlist(true_tab4[11, 5])), "****")

names(true_tab4) <- c("Uncertainty Av",
                      "Ambiguity Av",
                      "Compound Av",
                      "Reduction Av",
                      "Ambiguity Av ")

tab4_gt <- gt(true_tab4,
              rowname_col = c("Uncertainty Av",
                              "Ambiguity Av",
                              "Compound Av",
                              "Reduction Av",
                              "Ambiguity Av "),
              rownames_to_stub = TRUE,
              auto_align = "FALSE")

tab4_gt <- tab4_gt %>% 
  tab_header(title = md("**Table S4. Attitudes to Uncertainty and Compound Lotteries**")) %>%
  opt_align_table_header(align = c("center")) %>%
  cols_label("Uncertainty Av" = html("(1) <br>Uncertainty Av"),
             "Ambiguity Av" = html("(2) <br>Ambiguity Av"),
             "Compound Av" = html("(3) <br>Compound Av"),
             "Reduction Av" = html("(4) <br>Reduction Av"),
             "Ambiguity Av " = html("(5) <br>Ambiguity Av")) %>%
  tab_source_note(source_note = md("2SLS regression. Controls included for gender, order, and intelligence.")) %>%
  tab_source_note(source_note = md("Standard errors in parentheses")) %>%
  tab_source_note(source_note = c("* p < 0.10, ** p < 0.05, *** p < 0.01, **** p < 0.001"))

tab4_gt

#tab4_gt %>% gtsave(filename = "tab4_gt_fall_2022.html")
```


#### Checking constant error variance assumption
```{r}
library(performance)
#residuals2 are the residuals from the second stage regression
plot(col1_tab_4_2sls$fitted.values, col1_tab_4_2sls$residuals2,
     main = "Col1 of Tabel S4 Std. Residuals vs. Fitted Values",
     xlab = "Fitted Values",
     ylab = "Std. Residuals")
abline(h = 0, col = "red")
check_heteroskedasticity(col1_tab_4_2sls) # A p-value < 0.05 indicates non-constant variance (heteroskedasticity)

plot(col2_tab_4_2sls$fitted.values, col2_tab_4_2sls$residuals2,
     main = "Col2 of Tabel S4 Std. Residuals vs. Fitted Values",
     xlab = "Fitted Values",
     ylab = "Std. Residuals")
abline(h = 0, col = "red")
check_heteroskedasticity(col2_tab_4_2sls)

plot(col3_tab_4_2sls$fitted.values, col3_tab_4_2sls$residuals2,
     main = "Col3 of Tabel S4 Std. Residuals vs. Fitted Values",
     xlab = "Fitted Values",
     ylab = "Std. Residuals")
abline(h = 0, col = "red")
check_heteroskedasticity(col3_tab_4_2sls)

plot(col4_tab_4_2sls$fitted.values, col4_tab_4_2sls$residuals2,
     main = "Col4 of Tabel S4 Std. Residuals vs. Fitted Values",
     xlab = "Fitted Values",
     ylab = "Std. Residuals")
abline(h = 0, col = "red")
check_heteroskedasticity(col4_tab_4_2sls)

plot(col5_tab_4_2sls$fitted.values, col5_tab_4_2sls$residuals2,
     main = "Col5 of Tabel S4 Std. Residuals vs. Fitted Values",
     xlab = "Fitted Values",
     ylab = "Std. Residuals")
abline(h = 0, col = "red")
check_heteroskedasticity(col5_tab_4_2sls)


```


#### K-fold cross validation - 10 folds
```{r}
k <- 10
folds <- sample(k, length(renormalized_dat$ambiguity_i), replace = TRUE) 

metrics <- matrix(NA, nrow = k, ncol = 2)
for(i in seq_len(k)){

  is_train <- folds == i
  head(is_train)
  is_test <- !is_train

  train_df <- renormalized_dat[is_train, ]
  test_df <- renormalized_dat[is_test, ]

  mod1 <- ivreg(formula = ambiguity_i ~ risk_1_i +
                                        common_l_1_i +
                                        allais_1_i +
                                        end_new_1_i +
                                        loss_aversion_i +
                                        compound_1_i +
                                        raven_total +
                                        gender +
                                        backwards | raven_total +
                                        gender +
                                        backwards +
                                        risk_2_i +
                                        risk_3_i +
                                        common_l_2_i +
                                        allais_2_i +
                                        end_new_2_i +
                                        end_new_3_i +
                                        compound_2_i +
                                        compound_3_i +
                                        loss_aversion_i,
                                        data = renormalized_dat)
          
  y_hat <- predict(mod1, newdata = test_df)
  new_error <- na.omit((test_df$ambiguity_i - y_hat))

  mod2 <- ivreg(formula = ambiguity_i ~ risk_1_i +
                                        common_l_1_i +
                                        allais_1_i +
                                        end_new_1_i +
                                        loss_aversion_i +
                                        raven_total +
                                        gender +
                                        backwards | raven_total +
                                        gender +
                                        backwards +
                                        risk_2_i +
                                        risk_3_i +
                                        common_l_2_i +
                                        allais_2_i +
                                        end_new_2_i +
                                        end_new_3_i +
                                        loss_aversion_i,
                                        data = renormalized_dat)
  y_hat2 <- predict(mod2, newdata = test_df)
  new_error2 <- na.omit((test_df$ambiguity_i - y_hat2))

  metrics[i, 1] <- sqrt(mean(new_error)^2) # RMSE (Root Mean Squared Error)
  metrics[i, 2] <- sqrt(mean(new_error2)^2) # RMSE (Root Mean Squared Error)
}

# Finding that much of the variation is explained by Compound Av, removing Compound Av from the model increases the root mean square error. This suggests that the model with Compound Av is more accurate, as in closer to the the true value of uncertainty_i.
colnames(metrics) <- c("RMSE with compound av", "RMSE sans compound av")
comparing_metrics <- apply(metrics, 2, mean)
print(comparing_metrics)
```
